The \dealii{} Library, Version 9.2

### 2020-06-08 9.2/paper.tex
Distinguish const vs non-const interface
also acknowledge TACC for frontera access

        The interface of this class is designed to be minimal

@@

>>>>

        While providing a rich read-only interface, the non-const interface
        of this class is designed to be minimal

@@

The authors acknowledge the Texas Advanced Computing Center (TACC) at The
University of Texas at Austin for providing access to HPC resources that have
contributed to the research results reported within this paper.
